\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-10 Paper_honeypot.tex
gefixed .tex compiled nu wel

\begin{itemize}
\item Kippo

@@

It is not entirely unexpected that the username "root" is tried most ofted. 
We assume the username "w000t" is a backdoor user created in one or more exploits.
Interesting to note is that "jenny" is the name of a fake employee listed on the our honeypot website.
Most usernames were tried multiple times, even if they made no sense to us (for instance msnayeem_iitd tried to log in four times).

@@

\item HTTP
In three weeks, a total of 76002 HTTP-requests were received by our Apache server originating from 176 unique IP addresses. 4369 of these requests were 404'd.

@@

\section{Conclusion}
\label{Conclusion}
From Section \ref{Connection} we can conclude that...

>>>>

\subsection{Kippo}

@@

It is not entirely unexpected that the username "root" is tried most ofted. 
We assume the username "w000t" is a backdoor user created in one or more exploits.
Interesting to note is that "jenny" is the name of a fake employee listed on the our honeypot website.
Most usernames were tried multiple times, even if they made no sense to us for instance msnayeem\_iitd tried to log in four times.

@@

\subsection{HTTP}
In three weeks, a total of 76002 HTTP-requests were received by our Apache server originating from 176 unique IP addresses. 4369 of these requests were 404'd.

@@

\section{Conclusion}
\label{Conclusion}
From Section \ref{Connection} we can conclude that our honeypot was not as popular as we had hoped it would be. Because we chose not to advertise, we solely relied on the hackers abilities to find us by for example portscans. The number of attacks on us was therefore not high and neither was the depth of the attacks.
